Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-20 paper/main.tex
rewrite beginning of results

\begin{itemize}
    \item allgemein kürzen; insb. individual results kürzen
    \item consistencies across contrasts ausformulieren
    \item control contrasts ausformulieren
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

% level 1 and 2; similarly to the reviewed studies that employed designed
% stimuli; we "based on stimulus annotations"
We tested our modeled hemodynamic responses by conducting standard
two-level general linear model (GLM) analyses to create subject-specific results
($Z$-maps) across the 8 segments for every subject and each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

\paragraph{PPA Contrasts}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted
blocks of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

\paragraph{Control contrasts}

% intro
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. results and discussion}
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory cue of switching to another
setting.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) [time series were aligned to] via linear transformation to a
subject-specific, study-specific T2* template (cf.
\citep{sengupta2016extension}) and,
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

\paragraph{2nd level}

@@

\paragraph{3rd level}

@@

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was defined using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used static pictures.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess the performance of a naturalistic
auditory stimulus as a substitute for a visual paradigm to localize the
PPA.\todo{``localize''}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts for both naturalistic stimuli can be found
at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

% intro
First, we tested if results of a whole-brain analysis based stimulus annotations
would lead to increased hemodynamic activity in the PPA.

\subsubsection{group}
% AV intro
First, we analyzed data from the audio-visual movie offering visual but
ecologically more valid stimulation.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises, parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD intro
Second, we analyzed data from the movie's audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, the clusters of the current analysis are at the borders of the
posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
lingual gyrus.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

\subsubsection{individuals}

\todo[inline]{imo no need to mention it here but mention in discussion that
results are not driven by outliers when discussing ``localization'' performance}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects.
%
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize ``visual area'' in individual subjects and thus
possibly substitute a visual paradigm using blocks of pictures.

\todo[inline]{following is probably the part that Simon considered as en
passant}

\todo[inline]{if we here report procedure of Sengupta as detailed as
it is now, we probably need to explain the differences between strict, relaxed,
simple in more detail in the method section and not just reference to Sengupta}

% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% Sengupta: procedure a)
Starting with the most conservative contrast (strict set) and a threshold of t =
2.5, we looked for clusters with at least 20 voxels (using AFNI).
%
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the relaxed
set, or finally the simple set, and repeated the process until we found a
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

% naturalisti stimuli: intro
In the current study, time series of all subjects were analyzed both in subject
space and group space.
% subject space -> NeuroVault
Results of the analyses that were performed in each subject's [subject-]space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}. \todo{still
private collection}
% here report in group space
For better comparions of subjects, we here report results from the analyses
performed in group space. % ($z$-maps; Z>3.4, p<.05 cluster-corrected).
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to the procedure in \citep{sengupta2016extension}, we used the same
contrast of each naturalistic stimulus and the same threshold (Z>3.4, p<.05
cluster corrected) for all subjects.

>>>>

\begin{itemize}
    \item allgemein kürzen; insb. individual results kürzen
    \item consistencies across contrasts ausformulieren
    \item control contrasts ausformulieren
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level general linear model (GLM) analyses to create
subject-specific results ($Z$-maps) across the 8 segments for every subject and
each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. results and discussion}
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory cue of switching to another
setting.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}) and,
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

@@

% study goal
The goal of this study was to investigate if annotated cues about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was defined using a visual localizer experiment within
the same subjects \citep{sengupta2016extension}.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses  of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from the visual localizer.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.\todo{``localize''}
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template can
found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
\todo{still private collection}

@@

% AV intro
First, we analyzed data from the audio-visual movie offering a visual but
ecologically more valid stimulation.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

\paragraph{individual results}

\todo[inline]{if we here report procedure of Sengupta as detailed as it is now
(imo too long), we probably need to explain the differences between strict,
relaxed, simple in more detail in the method section and not just reference to
Sengupta}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.\todo{if you know what I mean}
% AD is the real shit
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize the PPA in individual subjects and thus
possibly substitute a visual paradigm [using blocks of pictures].

% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (strict set) and a threshold of t =
2.5, we looked for clusters with at least 20 voxels (using AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the relaxed
set, or finally the simple set, and repeated the process until we found a
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

% naturalisti stimuli: intro
In the current study, time series of all subjects were analyzed both in subject
space (Z>2.3, p<.05 cluster-corrected) and group space ).
% subject space -> NeuroVault
Results of the analyses that were performed in each subject's [subject-]space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found in the accompanying datset \todo{Neurvault does not like
unstandardized spaces}
% here report in group space
For better comparions of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected)
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to the procedure in \citep{sengupta2016extension}, we used the same
contrast of each naturalistic stimulus and the same threshold [(Z>3.4, p<.05
cluster corrected)] for all subjects.
